---
title: "week6_codealong"
author: "Kristin Gill"
date: "11/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```

# Mann-Whitney U wilcox.test()

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)

hist(gp_1)
hist(gp_2)

my_mwu <- wilcox.test(gp_1, gp_2)
my_mwu
```

# ggplot of palmer penguins flipper length vs. body mass

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point()

# linear model
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)
summary(penguin_lm)

# get the linear equation
penguin_lm_tidy <- broom::tidy(penguin_lm)

penguin_int <- penguin_lm_tidy$estimate[1]
penguin_int

penguin_coef <- penguin_lm_tidy$estimate[2]
penguin_coef

penguin_lm_out <- broom::glance(penguin_lm)
penguin_lm_out
```
### Example of how to write a statement that can automatically update variables

"Simple linear regression was used to explore the relationship between penguin flipper length (mm) and body mass (g) across all three penguin species, and including both male and female penguins. A significant regression model was found ($\beta$ = `r round(penguin_coef,3)`, F(`r penguin_lm_out$df`,`r penguin_lm_out$df.residual`) = `r round(penguin_lm_out$statistic,1)`, p < 0.001) with an R^2^ of `r round(penguin_lm_out$r.squared,3)`."

### Explore model assumptions
```{r}
plot(penguin_lm)
```

## Visualize the model
```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm",
              color = "red",
              size = 0.5,
              fill = "gray10",
              alpha = 0.5) + 
  theme_light() +
  ggpubr::stat_regline_equation(label.x = 180, label.y = 5700)

# Pearson's r, correlation
penguins_cor <- cor.test(penguins$flipper_length_mm, penguins$body_mass_g)
```

Here, we see that there is a strong positive correlation between penguin flipper length and body mass (*r* = `r round(penguins_cor$estimate,2)`, t(`r penguins_cor$parameter`) = `r round(penguins_cor$statistic,2)`, p < 0.001).